### 2019-07-18 manuscript/introduction.tex
Oops! Fixing the opening quote and adding its reference! - adding final sentence emphsizing the same statement from honoree Barrett

\begin{quote}
\em{``Among life history traits, reproductive characters that determine mating system patterns are perhaps the most influential in governing macroevolution." 
}
\\
\hspace*{\fill}\rm{ Barrett et al. (1996)}
\end{quote}

>>>>

\begin{quote}
\em{``Among life history traits, reproductive characters that determine mating patterns are perhaps the most influential in governing macroevolution." 
}
\\
\hspace*{\fill}\rm{ Barrett et al. (1996)}
\end{quote}
